Index measures for oak decline severity using phenotypic descriptors

### 2020-07-16 manuscript/manuscript.Rmd
fixed keywords
fixed summarise message outputs

**Keywords:** acute oak decline, chronic oak decline, phenotyping, machine learning, unsupervised learning, random forest, decline spectrum

@@

```{r stem_symptom_ranges}
symptom_ranges <- site_corrected_analysis_suitable_data %>%
  select(`Active bleed length (mm)`,`Black staining length (mm)`) %>%
  gather(descriptor,value) %>%
  group_by(descriptor) %>%
  summarise(minimum = min(value),
             maximum = max(value),
             center = minimum + (maximum - minimum) / 2
             )
```

>>>>

**Keywords:** Acute Oak Decline, Chronic Oak Decline, phenotyping, machine learning, unsupervised learning, random forest, decline spectrum

@@

```{r stem_symptom_ranges}
symptom_ranges <- site_corrected_analysis_suitable_data %>%
  select(`Active bleed length (mm)`,`Black staining length (mm)`) %>%
  gather(descriptor,value) %>%
  group_by(descriptor) %>%
  summarise(minimum = min(value),
            maximum = max(value),
            center = minimum + (maximum - minimum) / 2,
            .groups = 'drop'
  )
```
